Social Computing Article\thanks{This title is temporary}

### 2013-01-21 Article.tex
Arrumei detalhes que não estavam atualizados e complementei algumas sessões

\cite{mason:collablearnet} also provided important insights to human cooperation. However, since our basis is the work of~\cite{farenzena:collabem} we will use the former's results only as secondary support.

@@

We have developed and detailed a novel method for artificial social problem solving which draws inspiration from the {\em Memetic Networks} model proposed by~\cite{araujo:memenet}. It was used to build a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them. For simplicity, we limited our experiments to the {\em Sudoku} problem. Our goal is verifying whether the strategies employed by humans are competitive with other heuristics. After identifying the points in which those are lacking, we will then propose methods to increase the efficiency of human problem-solving networks.

@@

@@

 		\If{random(0,1) $<$ copyRate}
 		{
 			$A_{i}$.solution = selectedMessage\;
 		}
 	}
 	\For{i = 1 to N}
 	{
 		\CommentSty{ //Cognitive Stage }\;
 		$A_{i}$ = $i_{th}$ agent\;
 		Add local changes to $A_{i}$'s solution%$A_{i}$.solution = addLocalChanges($A_{i}$.solution)\;
 	}
 }
 \caption{No name yet}
\end{algorithm}

@@

The experiments conducted by~\cite{farenzena:collabem} point out a series of observations about the dynamics of cooperation in problem solving with human beings. For instance, the authors analysis has shown that human subjects are more likely to engage in the behaviour of copying the most readily available solutions on the graphic interface than in that of copying the most complete solutions. In order to analyse and compare these two behaviours, he have modelled each one of them as a message-selecting metric for the {\em Social Stage}.

@@

This metric employs the intuitive strategy of selecting the most complete message for copying. In the specific case of {\em Sudoku} solving, this metric selects the most filled {\em Sudoku} partial solution. Put in other words, it selects the {\em Sudoku} partial solution with the lesser number of blank cells.

@@

@@

{\em Sudoku} solving techniques are abundant in {\em Sudoku} strategy literature. Davis ~\cite{davis:mathsudoku} discusses a collection of these techniques, of which the {\em Naked Singles} rule, the {\em Hidden Singles} rule and the {\em Naked Twins} rule are some examples. These techniques intend to, given a partial {\em Sudoku} solution, generate a set of {\em movements} which can be used to mark cells of this {\em Sudoku} puzzle. We implemented $5$ of these rules, modelling each one of them as a function that maps a {\em Sudoku} partial solution to a set of {\em movements}. These functions can be used in the {\em Cognitive Stage} to add local changes to the {\em Sudoku} message received in the {\em Social Stage}.

The rules implemented were the {\em Unique Missing Candidate} rule, the {\em Naked Singles} rule, the {\em Hidden Singles} rule, the {\em Two out of Three} rule and the {\em Naked Twins} rule, all of which (with the exception of the {\em Two out of Three} rule) are discussed in~\cite{davis:mathsudoku}. In our modelling, each agent knows a particular quantity of rules, this quantity determining the agent's {\em level}. Our tests were all conducted with a heterogeneous population of agents of different {\em levels}. We detail below the 'two out of three' rule. For details on the other $4$ rules, see ~\cite{davis:mathsudoku}.

@@

\subsection{Conformist Behaviour}

We introduce in our modelling the {\em conformist} behaviour proposed by~\cite{cefferson:conformists} and further studied by~\cite{farenzena:collabem}, which states that agents are likely to copy a particular solution when surrounded by neighbours that share this solution.

Our approach was to establish a {\em treshold} determining a minimum necessary quantity $N$ of neighbours sharing a particular solution. In our modelling, all agents with $N$ or more neighbours having a solution $s$ in common are programmed to copy solution $s$ from them.

@@

Automatic {\em Sudoku} solvers employing a backtracking algorithm are easily programmed and very time-efficient. On the other hand, the space complexity of these algorithms is a barrier to most human solvers, who need to write down tons of observations in order to employ a backtracking strategy. With this in mind, we propose in our modelling two different kinds of backtracking, intended to be more similar to the way human beings employ error correction in {\em Sudoku} solving in a collaborative environment such as the one analysed in~\cite{farenzena:collabem}.

\begin{itemize}

\item
Local Backtracking: When faced with one or more conflicts in its own solution, an agent simply erases the conflicting cells.
\item
Social Backtracking: When faced with one or more conflicts in its own solution, an agent copies a solution from one of its neighbours. In our modelling, this is done by raising the copy rate of this particular agent to $1$.

\end{itemize}

@@

@@

Regarding our first hypothesis, our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the network's performance. To our surprise, however, they also indicate that guessing shows no signs of being detrimental to the process. On the contrary, in several cases it actually contributes to advancing the solution. The graphs in Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob} both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem. We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the {\em Sudoku} problem, not knowing the {\em Sudoku} solving rules needed to mark its cells. These agents have no hope solving the problem without some guessing mechanism, and take advantage of high {\em copy rates}, which can be used to correct wrong guesses through copying better agent's solutions.

@@

Of the three metrics employed by us in the \emph{Social Stage}, only one had the agent evaluate the content of the solutions proposed by their neighbours. Another chose who to copy based on position, simulating observed human behaviour~\cite{farenzena:collabem}, and the remaining one chose a neighbour randomly. Our hypothesis was that the first metric would perform better than the other two, a result which would confirm our belief that problem-solving social networks are able to respond positively to the employment of evaluation functions.

@@

Another explanation might be that humans might find difficult evaluating sudoku partial solutions. Although we have used the number of filled cells as a metric, that is not guaranteed to accurately measure which solution is best, since individuals might fill in cells with the wrong value. That hypothesis is supported by the experiments of~\cite{mason:collablearnet}, which used optimization of multidimensional functions as the problem being solved. This problem has a straightforward and accurate method of determining the fitness of a solution, which is simply the value of the given function for the proposed coordinates. In this experiments, the subjects seemingly did effectively evaluate the proposed solutions, giving preference to the ones that were better evaluated. The difference in behaviour between the two experiments might be because in the latter the fitness of a certain solution was obvious to the agent, while in the former it's not as easy to pick the best solution out of the available ones.

@@

Knowing that, systems that take advantage of human computation might take advantage of the computer aspect of human computation to encourage selection of better-evaluated solutions. One possibility is ordering the neighbours according to the quality of their solutions, with better-evaluated ones being displayed first, instead using a pre-specified or random order. However, that might introduce an overhead in the system, while also limiting variability and discouraging individuals that might have eventual more effective evaluation techniques. To avoid that, perhaps simply displaying the evaluation of each solution might be enough to encourage that behaviour.

@@

We compared results from social computing experiments done with human subjects with agent-based simulations mimicking the same problem-solving environments. To do this, we proposed a novel method for artificial social problem-solving and used it to model the {\em Sudoku} problem-solving environment studied by~\cite{farenzena:collabem}. We reached important conclusions concerning the dynamics of problem-solving collaborative environments: the behaviours of copying and guessing are shown to be beneficial to these systems. We also discuss the benefits of the behaviour of evaluating neighbours' solutions in order to select one of them for copying, rather than simply selecting a random solution or even the most readily available one, as the analysis conducted by~\cite{farenzena:collabem} has shown to be the case sometimes. With these results in mind, we conjectured that some proprieties of the graphic interface (as ordering the neighbours' solutions by the value of a evaluation function) could guide human subjects into the right direction, improving the performance of the social network. The validation of this hypothesis has been set as our future path and is currently being pursued.

>>>>

@@

We have developed and detailed a novel method for artificial social problem solving which draws inspiration from the {\em Memetic Networks} model proposed by~\cite{araujo:memenet}. It was then applied to build a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them. We limited our experiments to the {\em Sudoku} problem, which is more attractive and accessible to human beings while still remaining NP-complete and equivalent to SAT. Through that process, we compared the behaviour observed in humans with other strategies and reached the conclusion that it is detrimental to the problem-solving process. We verify that even an inaccurate metric of evaluation surpasses choosing an arbitrary neighbour to copy. In addition, we analyse the impact that copying and guessing have on the solving of the problem. After obtaining those results, we are able to propose a set of guidelines for the design of social problem-solving systems that might address those issues and improve the performance of human computing.

@@

 		\If{random(0,1) $<$ copyRate}
 		{
 			$A_{i}$.solution = selectedMessage\;
 		}
 	}
 	\For{i = 1 to N}
 	{
 		\CommentSty{ //Cognitive Stage }\;
 		$A_{i}$ = $i_{th}$ agent\;
 		Add local changes to $A_{i}$'s solution%$A_{i}$.solution = addLocalChanges($A_{i}$.solution)\;
 	}
 }
 \caption{Algorithm for the proposed model, encompassing the social and cognitive stages}
\end{algorithm}

@@

@@

The experiments conducted by~\cite{farenzena:collabem} point out a series of observations about the dynamics of cooperation in problem solving with human beings. For instance, the authors analysis has shown that human subjects are more likely to engage in the behaviour of copying the most readily available solutions on the graphic interface than in that of evaluating the available solutions and choosing the best according to some criterion. We have modelled three message-selecting strategies to employ in the \emph{Social Stage}, where the first attempts to evaluate the solutions and choose the best one, the second mimics the human behaviour of selecting the first solutions with greater probability and the third simply picks a neighbour at random to copy.

@@

This metric employs the intuitive strategy of selecting the most complete message for copying. In the specific case of {\em Sudoku} solving, this metric selects the most filled {\em Sudoku} partial solution. Put in other words, it selects the {\em Sudoku} partial solution with the least number of blank cells.

@@

\subsubsection{{\em Pick Random} metric}

This metric selects an arbitrary solution giving equal probability to each neighbour.

@@

{\em Sudoku} solving techniques are abundant in {\em Sudoku} strategy literature. Those techniques are based on the reasoning usually employed by humans to solve \emph{Sudoku} puzzles. Davis~\cite{davis:mathsudoku} discusses a collection of these techniques, of which the {\em Naked Singles} rule, the {\em Hidden Singles} rule and the {\em Naked Twins} rule are some examples. These techniques intend to, given a partial {\em Sudoku} solution, generate a set of {\em movements} which can be used to mark cells of this {\em Sudoku} puzzle. We implemented $5$ of these rules, modelling each one of them as a function that maps a {\em Sudoku} partial solution to a set of {\em movements}. These functions can be used in the {\em Cognitive Stage} to add local changes to the {\em Sudoku} message received in the {\em Social Stage}.

The rules implemented were the {\em Unique Missing Candidate} rule, the {\em Naked Singles} rule, the {\em Hidden Singles} rule, the {\em Two out of Three} rule and the {\em Naked Twins} rule, all of which (with the exception of the {\em Two out of Three} rule) are discussed in~\cite{davis:mathsudoku}. In our modelling, each agent knows a particular quantity of rules, this quantity determining the agent's {\em level}. Our tests were all conducted with a heterogeneous population of agents of different {\em levels}. We detail below the 'two out of three' rule. For details on the other $4$ rules, see~\cite{davis:mathsudoku}.

@@

@@

Automatic {\em Sudoku} solvers employing a backtracking algorithm are easily programmed and very time-efficient. On the other hand, the space complexity of these algorithms is a barrier to most human solvers, who need to write down tons of observations in order to employ a backtracking strategy. With this in mind, we propose in our modelling a different kind of backtracking, intended to be more similar to the way human beings employ error correction in {\em Sudoku} solving in a collaborative environment such as the one analysed in~\cite{farenzena:collabem}, which we refer to as \emph{social backtracking}. In it, when faced with one or more conflicts in its own solution, an agent copies a solution from one of its neighbours. In our modelling, this is done by raising the copy rate of this particular agent to $1$.

@@

We have proposed a model based on social psychology to simulate human behaviour in a problem-solving social network. Through it, we can simulate previous experiments performed on humans by modelling the observed behaviour as the cognitive and social stages. That will allow us to examine the consequences of that behaviour without having to enlist human subjects, which is usually expensive and time-consuming~\cite{?}. Moreover this model can be used as a guide of what to look for in the data collected by the experiments, in which the strategies employed by the subjects to solve the problem individually are mapped into the cognitive stage and the metric employed to pick a neighbour to copy, into the social stage.

We have applied the model into one such human computing experiment and reached particular conclusions about the methods employed by humans on it. Since the same behaviour was observed for different problems, we can expect these results to be generalized to a certain class of problems and systems with specific characteristics. We provide further analysis and details below.

@@

Regarding our first hypothesis, our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the network's performance. To our surprise, however, they also indicate that guessing shows no signs of being detrimental to the process. On the contrary, in several cases it actually contributes to advancing the solution. The graphs in Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob} both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem. We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the problem, not knowing the {\em Sudoku} solving rules needed to mark its cells. These agents have no hope solving the problem individually without some guessing mechanism, and the high {\em copy rates} allow them to correct wrong guesses through copying better agents' solutions.

@@

Of the three metrics employed by us in the \emph{Social Stage}, only one had the agent evaluate the content of the solutions proposed by their neighbours. Another chose who to copy based on position, simulating observed human behaviour~\cite{farenzena:collabem}, and the remaining one chose a neighbour randomly. Our hypothesis was that the first metric would perform better than the other two, a result which would confirm our belief that problem-solving social networks respond positively to the employment of evaluation functions.

@@

Another explanation might be that humans might find difficult evaluating sudoku partial solutions. Although we have used the number of filled cells as a metric, that is not guaranteed to accurately measure which solution is best, since individuals might fill in cells with the wrong value. That hypothesis is supported by the experiments of~\cite{mason:collablearnet}, which used optimization of a bidimensional function as the problem being solved. This problem has a straightforward and accurate method of determining the fitness of a solution, which is simply the value of the given function for the proposed coordinates. In this experiments, the subjects seemingly did effectively evaluate the proposed solutions, giving preference to the ones that were better evaluated. The difference in behaviour between the two experiments might be because in the latter the fitness of a certain solution was obvious to the agent, while in the former it's not as easy to pick the best solution out of the available ones.

Our experiments, however, have shown that although completeness is not necessarily an accurate measurement of quality, it was good enough to lead the network to the right solution. Not only that, it consistently performed better than the other strategies, even with high guess rates. That means that the incorrect guesses were successfully filtered out, allowing the correct solutions to prevail. Those results might extend to other constraint satisfaction problems that don't have an accurate method of evaluation. Therefore, it is not necessary for the problem addressed to have an exact metric to compare different possible solutions. An imperfect metric is good enough to be employed in a problem-solving social network.

Also,~\cite{mason:collablearnet} differed in that each player had exactly three neighbours. That fact allowed the players to see all of their neighbours at the same time in the interface, and limit their attention to less data.~\cite{farenzena:collabem} suggests that future experiments might prefer to limit their topology to smaller degrees, seeing as subjects tend to not look beyond their first few neighbours. It is possible for the large number of neighbours to have discouraged an in-depth evaluation of the solutions by the players.

@@

Considering the previous results, systems of human computation might take advantage of the interface to encourage selection of better-evaluated solutions. One possibility is to display the evaluation of each solution to encourage players to copy the ones with better score. However, the SAT experiments from~\cite{farenzena:collabem} actually assigned a score to each solution displayed to the users, who nevertheless chose according to position rather than evaluation. Another possibility is ordering the neighbours according to the quality of their solutions, with better-evaluated ones being displayed first, instead of using a pre-specified or random order.

The limitation on the network's degree suggested by~\cite{farenzena:collabem} and employed by~\cite{mason:collablearnet} is also promising, and displays evidence of success. Fewer connections allows for all neighbours to be displayed in the interface at once, without necessity of effort by the user by clicking buttons or scrolling. Moreover, humans might feel more encouraged to evaluate their neighbours if the number of possible solutions is limited.

@@

We compared results from social computing experiments done with human subjects with agent-based simulations mimicking the same problem-solving environments. To do this, we proposed a novel method for artificial social problem-solving and used it to model the {\em Sudoku} problem-solving environment studied by~\cite{farenzena:collabem}. We reached important conclusions concerning the dynamics of problem-solving collaborative environments: the behaviours of copying and guessing are shown to be beneficial to these systems. We also discuss the benefits of the behaviour of evaluating neighbours' solutions in order to select one of them for copying, rather than simply selecting a random solution or even the most readily available one, as the analysis conducted by~\cite{farenzena:collabem} has shown to be the case sometimes. With these results in mind, we conjectured that some properties of the graphic interface (as ordering the neighbours' solutions by the value of a evaluation function) could guide human subjects into the right direction, improving the performance of the social network. The validation of this hypothesis has been set as our future path and is currently being pursued.
